Reliable analytic approximation of pseudo-$\cl$ covariances

### 2019-05-20 draft/paper.tex
added more info about simulations

\newcommand{\pcl}[3]{\hat C_{#1}^{#2 #3}}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\fsky}{f_{\mbox{sky}}}
\newcommand{\clth}{C_l^{th}}
\newcommand{\clf}{C_l^{fore}}
\newcommand{\cl}{C_l}

@@

In order to generate the simulated $\cl$ we computed the correlations between
Gaussian fields obtained from a fiducial power spectra. The covariance
matrices were obtained from 20000 simulations, for the band powers determined
by the fraction of sky observed and the maximum band power we were able to
recover the fiducial power spectra for; i.e. $\sim 2 \times 512$. This
corresponds to $l_{\mbox{bpw}} = 1023$. For the lecture of the sky maps and
masks we used \textit{HEALPix}\footnote{\url{https://healpix.jpl.nasa.gov/}}
and
\textit{NaMaster}\footnote{\url{https://github.com/LSSTDESC/NaMaster}}~\cite{2018arXiv180909603A}
for the computation of the pseudo-$\cl$ and the covariances. Our code is
publicly available~\footnote{\url{https://github.com/damonge/PCLCovariance}}.

The same results are obtained even in the presence of foregrounds. In
particular, we tested the case with 100 foregrounds both at low scales and
large scales, adding a mock power spectra computed as $\clf = A (l +
1)^{\beta}$. Here, $A$ was fixed so that the ratio of the foreground power
spectra and the theoretical one ($\clth$) was $\clf/\clth = 0.1$ at $l=400$
and $\beta$ was randomly chosen from $U[-3, -1)$ for large scale effects and
fixed to $\beta = 0$ for small scale ones.

Apart from checking that we recover the same cosmological predictions from the
covariance matrices from both the analytical approximation and the
simulations, we studied the differences between them.

@@

>>>>

\newcommand{\pcl}[3]{\hat C_{#1}^{#2 #3}}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\fsky}{f_{\mbox{sky}}}
\newcommand{\clth}{C_l^{th}}
\newcommand{\clf}{C_l^{fore}}
\newcommand{\cl}{C_l}
\newcommand{\red}[1]{{\color{red} #1}}

@@

\subsection{Simulations}

Simulations were drawn from Gaussian fields that followed a fiducial power
spectrum. The fiducial cosmology (\red{For the 2-bin case}) is given by
$\Omega_{cdm} = 0.27$, $\Omega_b = 0.045$, $h = 0.67$, $A_s = 2.1 10^{-9}$ and
$n_s = 0.9$, where each term correspond, respectively, to the amount of cold
dark matter and baryons today, the reduced Hubble constant, the primordial
curvature fluctuation amplitude and the spectral index. The redshift bins are
shown in Fig.~\ref{fig:pz} and the theoretical $\cl$ are in
Fig.~\ref{fig:cl-2bins}. Since all parts of sky will not be equally observed, a
realist mask (see Fig.~\ref{fig:mask}) was applied.  The results shown here
were obtained using the same mas for each redshift bin, as it is expected to
be that way in real observations. We checked, however, that using different
masks yielded same results.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{./figures/pz.png}
  \caption{Galaxy distribution redshift bins.}
  \label{fig:pz}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{./figures/cls-sph-2b.png}
  \caption{Fiducial power spectra. We show only the $T$ and $E$ modes.}
  \label{fig:cl-2bins}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{./figures/mask-lss1.png}
  \caption{Example of sky mask used in our analysis}
  \label{fig:mask}
\end{figure}

The covariance matrices were obtained from 20000 simulations, for the band
powers determined by the fraction of sky observed and the maximum band power
we were able to recover the fiducial power spectra for; i.e. $\sim 2 \times
512$. This corresponds to $l_{\mbox{bpw}} = 1023$. To work with the sky
maps and masks we used
\textit{HEALPix}\footnote{\url{https://healpix.jpl.nasa.gov/}}, whereas 
\textit{NaMaster}\footnote{\url{https://github.com/LSSTDESC/NaMaster}}~\cite{2018arXiv180909603A}
was used for the computation of the pseudo-$\cl$ and the covariances. Our code
is publicly
available~\footnote{\url{https://github.com/damonge/PCLCovariance}}.

The same results are obtained even in the presence of foregrounds. In
particular, we tested the case with 100 foregrounds both at low scales and
large scales, adding a mock power spectra (e.g. Fig.~\ref{fig:fore}) computed as 
\begin{equation}
  \clf = A (l + 1)^{\beta}\,.
  \label{eq:fore}
\end{equation}
Here, $A$ was fixed so that the ratio of the foreground power spectra and the
theoretical one ($\clth$) was $\clf/\clth = 0.1$ at $l=400$ and $\beta$ was
randomly chosen from $U[-3, -1)$ for large scale effects and fixed to $\beta =
0$ for small scale ones.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{./figures/foreground.png}
  \caption{$\cl$ foregrounds used in order to check the reliability of the
    analytical approximations in their presence. They did not affect. The
    limiting cases for the large-scale contaminants are given by $\beta=-1,\,
    -3$ in Eq.~\ref{eq:fore}}
  \label{fig:fore}
\end{figure}

\subsection{$\chi^2$ distribution and covariance matrices}
Apart from checking that we recover the same cosmological predictions from the
covariance matrices from both the analytical approximation and the
simulations, we studied the differences between them.

@@

\appendix

\section{Flat sky}
